Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654

### 2016-05-15 WRITEUP/Intro.tex
reorganize paper --> ms.tex for real thing, Intro.tex is now where I dump text

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

\citestyle{aa}
\shorttitle{Something goes here}
\shortauthors{Leung \& Riechers}

\begin{document}
%{\tiny  \RevisionInfo}

\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
\end{abstract}

\keywords{ISM: molecular -- 
          infrared: galaxies -- 
          galaxies: starburst --
          galaxies: evolution}

  %--------------------------------------------------------------------------
  %                                Introduction
  %--------------------------------------------------------------------------

\section{Introduction}
% Role of ULIRG/Merger and AGN
Ultra-luminous IR galaxies \LIR\,$>$\,10$^{12}$\Lsun.. hot dust re-radiating energy from a central SB or an active galactic 
nucleus (AGN), i.e. expect them to have large gas to begin with to drives the \LIR.

% local --> merger
Current studies of local ULIRGs revealed a causal connection between ULIRG activity and galaxy interaction based on morphological evidence of ULIRGs e.g. have double nuclei, severely distorted isophotes, or strong tidal features.

@@

% but at least, we now understand/expect
In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the 
progenitors of the dormant SMBHs in nearby galaxies. Quasars are powered by gas falling into central BHs, when galaxies 
collide or merge, which is a natural consequence of hierarchical structure formation because During the early epoch, the 
universe was smaller.

@@

important to study gas dynamics from mergers because that's how we think gas accumulates and flow inward for SMBH grow
and merger drives turbulent gas motions, which fuel the central BH, and SB. 
Ideally, we would want to measure kinematics of e.g. CO, CII to trace the dynamical mass of QSO host galaxies
    - free from dust extinction as with optical

@@

% The source
The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
$z_\textrm{AGN,HST}$ =
0.658, respectively \citep{}

@@

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
% set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
% combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz)
with the Combined Array for Research in Millimeter-wave
Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) were 
carried out on 2014 February 17
under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations. The 3 mm receivers were used to cover the
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($\sim$17.9 km s$^{-1}$). The line was placed in the
lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
flagging poor visibility data.
The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks.
% poor phase note
Since the phase calibrator from the first track is faint and was observed under
poor weather and the phase calibrator used for the second track was
far from our target source.
Hence, the phase calibration was
subpar, with rms scatter $\sim$ 60\degr.
We estimate $\sim
$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and
the calibrated phase scatter.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

@@

% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
%  57.753459930419922        10.658399798838524
% 38.906448364257812        54.223567641493943
% 258.26144409179688        57.450322398332851
% 2.2153112888336182        2.9563491085933622

% If we fit gaussian without the continuum to minimize error:
% 58.848747253417969        10.030933764224825
% 36.368530273437500        54.749284630860281
% 276.93515014648438        54.753666156237443

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231.
We extract the spectrum and fit a single-component Gaussian as shown in Figure
\ref{fig:co32spec}
yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in 
the
calibration.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}
\caption{
CO32 line spectrum, looks like we are fitting to a bunch of noise. TODO
 \label{fig:co32spec}}
\end{figure}

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
velocity range in z=0 frame = [-530.33, 72.73] \kms
chan = [127, 155]
sigma = 0.16821825 Jy \kms per Beam
theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
 \label{fig:highOmoments}}
\end{figure}

@@

\section{gas kinematics and dynamics}
% data 1st moment map:
the observed velocity fields represents the rotation velocities.  
We note that the velocity field is likely affected by
systematic errors and by beam smearing given the spatial resolution of our data.

@@

% Interpretation of the lens model
- C06 suggest the presence of an interacting dusty galaxy in their HST
observations, which BJB+08 calls it the F component. The lensed images of the
ABCDE
components coincide with our CO data (see mom0 on HST and channel map),
evidently CO emission coming from the AGN host galaxy.
- one of the red channels in our lens model suggests a second source component,
which is consistent with the spatially offset dusty source (see mom0 on HST,
which
the red velocity component coincides with this F component)

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
of channel widths $\sim$ 100\kms.
\label{fig:}}
\end{figure*}

@@

%==============================================================================
%                                Back matters
%==============================================================================

% ACKNOWLEDGEMENTS
%-----------------
\acknowledgments
We thank...

  %--------------------------------------------------------------------------
  %                               Bibliography
  %--------------------------------------------------------------------------
\bibliographystyle{yahapj}
\bibliography{RXJ.bib}
\end{document}

>>>>

%%% this becomes dummy

\section{Introduction}
Ultra-luminous IR galaxies (ULIRGS; \LIR\,$>$\,10$^{12}$\Lsun) are extremely luminous
in the IR due to the re-radiation of energy absorbed from dust from starburst or an active galactic 
nucleus (AGN), which also implies a large gas content to begin with. % to drives these activities.

Current studies of local ULIRGs revealed a causal connection between ULIRG activity and galaxy interaction based on morphological evidence of ULIRGs e.g. have double nuclei, severely distorted isophotes, or strong tidal features.

@@

% and high-z
In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the 
progenitors of the dormant SMBHs in nearby galaxies. Quasars are powered by gas falling into central BHs, when galaxies 
collide or merge, which is a natural consequence of hierarchical structure formation because During the early epoch, the 
universe was smaller.

@@

important to study gas dynamics from mergers because that's how we think gas accumulates and flow inward for SMBH grow
and merger drives turbulent gas motions, which fuel the central BH, and SB. 
Ideally, we would want to measure kinematics of e.g. CO, CII to trace the dynamical mass of QSO 
host galaxies, free from dust extinction as with optical.

@@

% The source
The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
$z_\textrm{AGN,HST}$ =
0.658, respectively \citep{Sluse03a}

@@

\subsection{CARMA}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
% set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
% combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz)
with the Combined Array for Research in Millimeter-wave
Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) were 
carried out on 2014 February 17
under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations. The 3 mm receivers were used to cover the
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($\sim$17.9 km s$^{-1}$). The line was placed in the
lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
flagging poor visibility data.
The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks.
% poor phase note
Since the phase calibrator from the first track is faint and was observed under
poor weather and the phase calibrator used for the second track was
far from our target source.
Hence, the phase calibration was
subpar, with rms scatter $\sim$ 60\degr.
We estimate $\sim
$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and
the calibrated phase scatter.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

@@

% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
% 
% If we use FWHM of CO21 line to extract CO32 Intensity: I = Jy km/s over chan=[]

We detect resolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231.
We extract the spectrum as shown in Figure
\ref{fig:co32spec}.
The integrated line flux is 37.1$\pm$ 2.8 Jy km/s, this does not include the uncertainties in 
the
calibration.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
\caption{
CO32 line spectrum, looks like we are fitting to a bunch of noise. TODO
 \label{fig:co32spec}}
\end{figure}

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
 \label{fig:highOmoments}}
\end{figure}

@@

\section{gas kinematics and dynamics}
% Gas excitation

Based on the apparent intensity of  \cco and \bco, we find an excitation of BLAH, assuming differential lensing is negligible.

% data 1st moment map:
the observed velocity fields represents the rotation velocities.  
We note that the velocity field is likely affected by
systematic errors and by beam smearing given the spatial resolution of our data.

@@

% Interpretation of the lens model
\citet{Claeskens06a} suggest the presence of an interacting dusty galaxy in their HST
observations, which BJB+08 calls it the F component. The lensed images of the
ABCDE
components coincide with our CO data (see mom0 on HST and channel map),
evidently CO emission coming from the AGN host galaxy.
- one of the red channels in our lens model suggests a second source component,
which is consistent with the spatially offset dusty source (see mom0 on HST,
which
the red velocity component coincides with this F component)

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
of channel widths $\sim$ 100\kms.
Make this bigger in the future
\label{fig:}}
\end{figure*}

@@
